Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-06 paper.tex
turn table captions into titles

A pre-release of Cyclus version 1.4 was used for this analysis.  Archetypes
used were the standard ones provided with Cyclus in the included Cycamore
library - also a pre-release of version 1.4.  A custom storage archetype was
used because Cycamore did not yet provide one.  The standard cycamore reactor archetype
was used for both LWR and SFR reactor types in cases MI and QI.  Correspondingly
the custom fleet-based reactor archetype described earlier was used for both reactor
types in cases MF and QF.  Additional configuration for the reactor types is
shown in Table \ref{tab:reactors}.

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
            & LWR & SFR \\
        \hline                       
        Lifetime (yr)         & 80 & 80 \\
        Cycle length (months) & 18 & 14 \\
        Batch size (kg)       & 29565 & 7490 \\
        Batches per core      & 3 & 5 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \caption[Reactor facility parameters]{Reactor facility parameters. Cycle length includes the refueling outage.}
    \label{tab:reactors}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
                                                                             & LWR      & SFR      \\
        \hline                       
                                                                             &          &          \\
        Discharge Rate ($\frac{\text{kg} \cdot \text{HM}}{\text{month}}$)           & 1642.5   & 535      \\
                                                                             &          &          \\
        Burnup  ($\frac{\text{MWe} \cdot \text{month}}{\text{kg} \cdot \text{HM}}$) & 0.547945 & 0.672897 \\
                                                                             &          &          \\
        Effective Power  ($\text{MWe}$)                                      & 900      & 360      \\
                                                                             &          &          \\
        Core Size  ($\text{kg} \cdot \text{HM}$)                                    & 88695    & 40125    \\
                                                                             &          &          \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \caption[Reactor parameter invariants]{
        Reactor configuration invariants maintained across all four
        simulation cases.
    }

    \label{tab:invar}
\end{table}

\begin{table*}
    \centering
    \begin{tabular}{ |r | c c | c c | }
        \hline                       
                                          & \multicolumn{2}{c |}{LWR}       & \multicolumn{2}{c |}{SFR} \\
                                          & Cases MI,QI & Cases MF,QF (fleet) & Cases MI,QI & Cases MF,QF (fleet)  \\
        \hline                       
        Cycle length (months)             & 15        & 18                & 12        & 15 \\
        Refueling outage (months)         & 3         & 0                 & 3         & 0 \\
        Batch size ($\text{kg} \cdot \text{HM}$) & 29,565    & 29,565            & 8,025     & 40,125 \\
        Power capacity (MWe)              & 1,080     & 900               & 450       & 360 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \caption[Reactor parameters by case]{
        Reactor configuration for each of the four simulation cases.
    }

    \label{tab:reactor-detail}
\end{table*}

>>>>

A pre-release of Cyclus version 1.4 was used for this analysis.  Archetypes
used were the standard ones provided with Cyclus in the included Cycamore
library - also a pre-release of version 1.4.  A custom storage archetype was
used because Cycamore did not yet provide one.  The standard cycamore reactor archetype
was used for both LWR and SFR reactor types in cases MI and QI.  Correspondingly
the custom fleet-based reactor archetype described earlier was used for both reactor
types in cases MF and QF.  Additional configuration for the reactor types is
shown in Table \ref{tab:reactors} (cycle length includes the refueling outage).

@@

\begin{table}[h]
    \label{tab:reactors}
    \caption{Reactor Facility Parameters}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
            & LWR & SFR \\
        \hline                       
        Lifetime (yr)         & 80 & 80 \\
        Cycle length (months) & 18 & 14 \\
        Batch size (kg)       & 29565 & 7490 \\
        Batches per core      & 3 & 5 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
\end{table}

@@

\begin{table}
    \label{tab:invar}
    \captionsetup{justification=centering}
    \caption{Reactor Parameter Invariants}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
                                                                             & LWR      & SFR      \\
        \hline                       
                                                                             &          &          \\
        Discharge Rate ($\frac{\text{kg} \cdot \text{HM}}{\text{month}}$)           & 1642.5   & 535      \\
                                                                             &          &          \\
        Burnup  ($\frac{\text{MWe} \cdot \text{month}}{\text{kg} \cdot \text{HM}}$) & 0.547945 & 0.672897 \\
                                                                             &          &          \\
        Effective Power  ($\text{MWe}$)                                      & 900      & 360      \\
                                                                             &          &          \\
        Core Size  ($\text{kg} \cdot \text{HM}$)                                    & 88695    & 40125    \\
                                                                             &          &          \\
        \hline                       
    \end{tabular}
\end{table}

\begin{table*}
    \label{tab:reactor-detail}
    \centering
    \captionsetup{justification=centering}
    \caption{Reactor Parameters by Case}
    \begin{tabular}{ |r | c c | c c | }
        \hline                       
                                          & \multicolumn{2}{c |}{LWR}       & \multicolumn{2}{c |}{SFR} \\
                                          & Cases MI,QI & Cases MF,QF (fleet) & Cases MI,QI & Cases MF,QF (fleet)  \\
        \hline                       
        Cycle length (months)             & 15        & 18                & 12        & 15 \\
        Refueling outage (months)         & 3         & 0                 & 3         & 0 \\
        Batch size ($\text{kg} \cdot \text{HM}$) & 29,565    & 29,565            & 8,025     & 40,125 \\
        Power capacity (MWe)              & 1,080     & 900               & 450       & 360 \\
        \hline                       
    \end{tabular}
\end{table*}
